MLH1 data report 

### 2017-11-02 rmd_report.rmd
added factor order to the Funcs

```{r}
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
# sort your dataframe, by the focal categories
MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

@@

#count the non-quality measures,  #remove non qualit
#length(MLH1_data[ !(is.na(MLH1_data$quality) | MLH1_data$quality==""), ] )  #15 rows with out quality scores, remove.
MLH1_data <- MLH1_data[ !(is.na(MLH1_data$quality) | MLH1_data$quality==""), ]

MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]
```

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
kable(AP_strain_table)
```

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "black", "grey", "lightgrey"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```

>>>>

```{r}

#set the order of another column, based on another variable (so that when)

MLH1_data <- add_strain(MLH1_data)
MLH1_data$strain <- as.factor(MLH1_data$strain)

MLH1_data$strain<- factor(MLH1_data$strain,levels =c( "G", "WSB", "LEWES", 
                                                        "PWD", "MSM",
                                                       "CAST", "HMI",
                                                        "SPRET", "other"), order=T )

MLH1_data$sex<- factor(MLH1_data$sex,levels =c( "female", "male"), order=T )

MLH1_data$category<- factor(MLH1_data$category,levels =c( "G female", "G male", 
                      "WSB female", "WSB male", "LEWES female", 'LEWES male', "PERC male",
                      "PWD female", "PWD male", "MSM female", "MSM male",
                      "CAST female", "CAST male", "HMI female", "HMI male",
                      "SPRET female", "SPRET male"), order=T )

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, category, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

MLH1_data <- MLH1_data %>%
  arrange(category, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])

# sort your dataframe, by the focal categories
#MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

@@

#count the non-quality measures,  #remove non qualit
#length(MLH1_data[ !(is.na(MLH1_data$quality) | MLH1_data$quality==""), ] )  #15 rows with out quality scores, remove.
#MLH1_data <- MLH1_data[ !(is.na(MLH1_data$quality) | MLH1_data$quality==""), ]

#MLH1_by_F_strain <- MLH1_data[MLH1_data$sex == "female", ]
#MLH1_by_M_strain <- MLH1_data[MLH1_data$sex == "male", ]
```

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
#kable(AP_strain_table)
```

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= as.factor(strain)  )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey", "black" ))
ff <- ff   + facet_wrap(~ sex, scales="free")
ff

#
#scale_fill_brewer(palette="Dark2")
